\documentclass[aspectratio=169]{beamer}
\setbeamertemplate{navigation symbols}{}
\usepackage{color, amsmath, comment, subfigure}
\usepackage{url}

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}

%%%%%%%%%%%%%%%%%%%%%%%%%%
\title[]{Comments slides for Thursday, November 19:\\Privacy and ethics, part 2}
\author[]{Matthew J. Salganik}
\institute[]{}
\date[]{COS 597E/SOC 555 Limits to prediction\\Fall 2020, Princeton University}

\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%
\frame{\titlepage}
%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}

Obermeyer et al.\ and Benjamin
\begin{itemize}
\item Problem formulation (choice of outcomes) as a ``hidden'' limit to prediction (also source of overconfidence).  We might be able to predict GPA quite well, but we might really need to predict knowledge.  To the extent they are different, we might be fooling ourselves.  This seems like the basis for a toy model.
\pause
\item How does the choice of outcome relate to the goal?  Passive prediction vs prediction for intervention.  Cost vs avoidable costs.
\pause
\item One of the hardest part of this paper is getting access to the data and code.
\end{itemize}

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}

Chouldechova
\begin{itemize}
\item Fairness as a limit to predictive accuracy?  How much does one of these requirements reduce the best possible accuracy?
\end{itemize}

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}

Barbaras et al.
\begin{itemize}
\item I was so excited to read this paper . . . . \pause and it was OK.
\pause
\item I agree that improved predictive performance is the wrong metric. We want to show lives improved, crimes prevented, etc.
\pause
\item Want to avoid unmeasured costs
\pause
\item Hard to know how much prediction reshapes criminal justice
\pause
\item Do as I say vs do as I do
\pause
\item P.S. Interested in understanding how these systems impact practice: check out Simone Zhang's dissertation
\end{itemize}

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\frame{\titlepage}


\end{document}
